---
title: "mychoice"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{mychoice}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, warning=FALSE}
library(mychoice)
```
The tools in mychoice are designed to make it easier to develop and use choice models with the [ready4 youth mental health economic model](https://www.ready4-dev.com/docs/model/) (or any other model developed with the [ready4 framework](https://www.ready4-dev.com)).

This development version of the mychoice package has been made available as part of the process of testing and documenting the package. 

Currently there are no vignettes available. However, examples of the application of mychoice functions to a real world discrete choice experiment are in programs available at https://doi.org/10.5281/zenodo.6626256 (design of a discrete choice experiment survey) and https://doi.org/10.5281/zenodo.7223286 (analysis of discrete choice experiment survey responses). PDF versions of each program, along with the artefacts produced by each are available in the online dataset at https://doi.org/10.7910/DVN/VGPIPS. 
